\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-09-01 analysis/paper/paper.Rmd
updated pdf formatting
line numbers and removed the kaywords and highlights

---
title: "Species & genus plant classification with NEON hyperspectral data"
author:
  - Victoria Scholl\thanks{victoria.scholl@colorado.edu, Earth Lab and Geography Dept., University of Colorado, Boulder, CO 80303, USA}
  - Maxwell B. Joseph\thanks{maxwell.b.joseph@colorado.edu, Earth Lab, University of Colorado, Boulder, CO 80303, USA}

#date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    includes:
      in_header: header.sty
bibliography: references.bib
csl: "ecology.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

@@

# Introduction

@@

# Background

# Methods

## Data cleaning

## Species classification

## Genus classification

@@

# Results

@@

# Discussion

# Conclusion

# Acknowledgements

@@

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

@@

Figure 1 info...

>>>>

---
title: \textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

author:
  - Victoria Scholl\thanks{victoria.scholl@colorado.edu, Earth Lab and Geography Dept., University of Colorado, Boulder, CO 80303, USA}
  - Maxwell B. Joseph\thanks{maxwell.b.joseph@colorado.edu, Earth Lab, University of Colorado, Boulder, CO 80303, USA}

output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    includes:
      in_header: header.sty
bibliography: references.bib
csl: ecology.csl 
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  dpi = 300
)
```

@@

\linenumbers

\begin{abstract}
Abstract text here
\end{abstract}

```{r, results='hide', message=FALSE, include=FALSE}
# Run the main analysis
```

# Introduction {-}

@@

# Background {-}

# Methods {-}

## Data cleaning {-}

## Species classification {-}

## Genus classification {-}

@@

# Results {-}

@@

# Discussion {-}

# Acknowledgements {-}

@@

# References {-}

@@

Figure 1 description...
